### 2018-10-04 paper/paper.tex
improvement of time span definition

Let the periodic demand be given by $\di{t}{t+1} = \max(0,\dmean(\frac{t+t+1}{2}) + \epsilon)$,
where $\dmean$ is a function which maps any given time $t \geqslant 0$ to the expected mean demand
at time $t$ and $\epsilon$ is drawn from a random variable $\X$ with mean $0$ and standard deviation
$\sigma$.

\begin{example}
  In case of a constant demand, $\dmean$ maps to a constant value, whereas for a seasonal demand $f$
  could be the sine-function.
  % In most cases we expect the random variable to be drawn from the
  % standard distribution $\X \sim \N{0}{\sigma^{2}}$ and in case of a discrete demand space applying
  % the nearest integer function.
\end{example}

% \MS{needed at all? we got the variance. But the max operator is used?}
% \begin{definition}
%   We define the \emph{standardised demand} $\dl{t}$ with time $t \geqslant 0$ as $\dl{t} \defsym
%   \di{t}{t+1} - \dmean(\frac{2t+1}{2})$. That is we subtract the mean from the demand to
%   be able to investigate the deviations solely.
%   % \begin{align*}
%   %   \dl{t} \defsym
%   %   \begin{cases}
%   %     1 + \epsilon & \text{iff }\dmean(\frac{2t+1}{2}) = 0\\
%   %     \dmean^{-1}(\frac{2t+1}{2}) \cdot \dmean(\frac{2t+1}{2}) + \epsilon & \text{otherwise}
%   %   \end{cases}
%   %   \tpkt
%   % \end{align*}
%   % Note that $\dmean(\cdot)$ is a scalar value and thus the inverse $\dmean^{-1}(\cdot)$ exists
%   % unless the mean demand is $0$.
% \end{definition}
% The standardised demand allows us to extract useful information from the deviations of the

We use the standard deviation $\sigma$ of the random variable $\X$ as measure for estimating the
time span being considered in our model. Recall that the standard deviation measures the expected
deviation of the mean in orders for one period.
%
Futhermore,... \MS[t]{seasonal stuff}
%

\begin{definition}
  We define the time span $\ts$ of the manufacturing system under investigation as
  \begin{align*}
    \ts \defsym \MS[t]{\text{seasonal stuff todo}} + \z \cdot 2 \sigma \tcom
  \end{align*}
  where $\z$ is a parameter.
\end{definition}

>>>>

\begin{definition}
  The \emph{periodised demand} $\dper{p}$ for any period $p \in \Nat$ is given by
  $\dper{p} = \max(0,\dmean(\frac{p+p+1}{2}) + \epsilon) = \di{p}{p+1}$, where $\dmean$ is a
  function which maps any given period to the expected mean demand at this period and $\epsilon$ is
  drawn from a random variable $\X$ with mean $0$ and standard deviation $\sigma$. Note that $f$
  must not necessarily be continuous.
  % Note that the periodised demand is only defined over natural numbers, which describe the current
  % period.
\end{definition}

\begin{example}
  In case of a constant demand, $\dmean$ maps to a constant value and $\epsilon = 0$, whereas for a
  seasonal demand $f$ in a continuous space one may use the sine-function and
  $\X \sim \N{0}{\sigma^{2}}$.
  %
  \MS[t]{maybe refer to inventory control, as there $\N{0}{\cdot}$ is also used?}

  % In most cases we expect the random variable to be drawn from the
  % standard distribution $\X \sim \N{0}{\sigma^{2}}$ and in case of a discrete demand space applying
  % the nearest integer function.
\end{example}

In practise the available demand data is used to infer the function $\dmean$ and the value for
$\sigma$. This could be done using regression and statistical analyses. Therefore, in hereafter
these values are expected to be known.

% \MS{needed at all? we got the variance. But the max operator is used?}
% \begin{definition}
%   We define the \emph{mean deviation demand} $\ddev{t}$ with time $t \geqslant 0$ as
%   $\ddev{t} \defsym \di{t}{t+1} - \dmean(\frac{2t+1}{2})$. That is we subtract the mean from the
%   demand to be able to investigate the deviations solely.
%   % \begin{align*}
%   %   \ddev{t} \defsym
%   %   \begin{cases}
%   %     1 + \epsilon & \text{iff }\dmean(\frac{2t+1}{2}) = 0\\
%   %     \dmean^{-1}(\frac{2t+1}{2}) \cdot \dmean(\frac{2t+1}{2}) + \epsilon & \text{otherwise}
%   %   \end{cases}
%   %   \tpkt
%   % \end{align*}
%   % Note that $\dmean(\cdot)$ is a scalar value and thus the inverse $\dmean^{-1}(\cdot)$ exists
%   % unless the mean demand is $0$.
% \end{definition}
% The standardised demand allows us to extract useful information from the deviations of the

The higher the standard deviation of the demand, the more likely it is to find high fluctuations in
the release pattern. Thus, the scaled deviations in the demand specify a natural lower-bound of
release decisions to consider in the analysis of the \LTS{}.
%
Hence, we use the standard deviation $\sigma$ of the random variable $\X$ in relation to the mean
demand as measure for determining the time span being considered. Recall that the standard deviation
measures the expected deviation of the mean in orders.
%
%
% Thus, $2 \sigma$ specify the (minimum) expected deviation of the demand and thus also the release
% decisions from one period to the next.
%
Futhermore,... \MS[t]{seasonal stuff}
%

\begin{definition}
  We define the \emph{time span} $\ts(p)$ in period $p$ of the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \ts(p) \defsym 1 + \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}} +
    \MS[t]{\text{seasonal stuff todo}} \tcom
  \end{align*}
  where $\zs$ is a scaling parameter for specifying the confidence interval being considered. This
  definition assumes a symmetric probability distribution of $\X$ in the second term. For asymmetric
  probability distributions, the definition can be easily extended to integrate
\end{definition}

The reduce the impact of outliers we average the actual releases over $k$ values.
